\documentclass[a4paper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome5}

% Custom commands
\newcommand{\twocolentry}[2]{
    \noindent\textbf{#2} \hfill \textit{#1}
}

\newcommand{\onecolentry}[1]{
    \noindent #1 \par
}

\newenvironment{highlights}{
    \begin{itemize}[leftmargin=1.5em]
}{
    \end{itemize}
}

\newenvironment{cvitems}{
    \begin{itemize}[leftmargin=1.5em]
}{
    \end{itemize}
}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

% Header
\begin{center}
    {\LARGE \textbf{Amina Liaquat}}\\
    \vspace{0.3cm}
    Faisalabad, Pakistan \\
    \vspace{0.2cm}
    \href{mailto:aminaliaquat259@gmail.com}{\faEnvelope\ aminaliaquat259@gmail.com} \quad
    \faPhone\ 0311-1482812 \\
    \href{https://www.linkedin.com/in/amina-liaquat}{\faLinkedin\ Amina Liaquat} \quad
    \href{https://github.com/amina-liaquat56}{\faGithub\ amina-liaquat56} \quad
    \href{https://leetcode.com/u/amina_liaquat04/}{\faCode\ amina\_liaquat04}
\end{center}

\vspace{0.4cm}

% About Me
\section*{About Me}
\onecolentry{
I'm Amina Liaquat. I'm currently pursuing my MS in Computer Science at the University of Agriculture, Faisalabad. I'm learning how to code. I love making and designing webpages with HTML and CSS (and sometimes JavaScript). It's fun to code something that anyone on the web can easily see. I also enjoy programming in JavaScript and Python because they challenge me more. I love it when I can finally solve a difficult problem.
}

% Education
\section*{Education}

\twocolentry{Jan 2024 – Dec 2025}{University of Agriculture Faisalabad}\\
\onecolentry{\textit{MS in Computer Science}}\\
\begin{highlights}
    \item CGPA: 3.2 / 4.0
\end{highlights}

\twocolentry{Sep 2019 – Oct 2023}{Government College University, Faisalabad}\\
\onecolentry{\textit{BS in Computer Science}}\\
\begin{highlights}
    \item CGPA: 3.5 / 4.0
\end{highlights}

% Achievements
\section*{Achievements}

\begin{cvitems}
    \item \textbf{\textcolor{blue}{LeetCode:}} Solved \textbf{130+} Data Structures and Algorithms problems – \href{https://leetcode.com/u/amina_liaquat04/}{Profile Link}
    
    \item \textbf{\textcolor{blue}{CS50x Puzzle Day Winner (2×):}} 
    \href{https://ik.imagekit.io/fjchcwc5f/WhatsApp%20Image%202025-07-06%20at%2010.53.51%20AM.jpeg?updatedAt=1751781535212}{Won 1st place} at Harvard CS50x Puzzle Day 2024 and 2025 by solving 9/9 complex puzzles.
\end{cvitems}

% Skills
\section*{Skills}

\onecolentry{\textbf{Languages:} HTML5, CSS3, Bootstrap, Python, PHP, JavaScript}
\vspace{0.2cm}

\onecolentry{\textbf{IDEs:} VS Code, PyCharm, Anaconda, Jupyter Notebook, MATLAB}
\vspace{0.2cm}

\onecolentry{\textbf{Version Control:} Git, GitHub}

% Projects
\section*{Projects}

\twocolentry{\href{https://github.com/amina-liaquat56/Testimonial-box-switcher.git}{GitHub Repo}}{Testimonial Box Switcher}
\begin{highlights}
    \item A lightweight testimonial switcher built using HTML, CSS, and JavaScript.
    \item Displays user testimonials with auto-switching and smooth transitions.
\end{highlights}

\twocolentry{\href{https://github.com/amina-liaquat56/Calculator.git}{GitHub Repo}}{Calculator}
\begin{highlights}
    \item Developed a responsive calculator with modern UI using HTML, CSS, and JavaScript.
\end{highlights}

\twocolentry{2025}{Personal Projects}
\begin{highlights}
    \item Built an E-commerce website, Netflix mobile navigation UI, and calculator.
    \item Tools Used: HTML, CSS, JavaScript
\end{highlights}

\end{document}
